\documentclass[
	% -- opções da classe memoir --
	12pt,				% tamanho da fonte
	openright,			% capítulos começam em páginas ímpar (insere página vazia caso preciso)
	oneside,			% para impressão em verso e anverso. Oposto a oneside
	a4paper,		% tamanho do papel.
	% -- opções da classe abntex2 --
	chapter=TITLE,		% títulos de capítulos convertidos em letras maiúsculas
	section=TITLE,		% títulos de seções convertidos em letras maiúsculas
	%subsection=TITLE,	% títulos de subseções convertidos em letras maiúsculas
	%subsubsection=TITLE,% títulos de subsubseções convertidos em letras maiúsculas
	% -- opções do pacote babel --
    brazil,				% o último idioma é o principal do documento
	english,			% idioma adicional para hifenização
	%french,			% idioma adicional para hifenização
	%spanish,			% idioma adicional para hifenização
	sumario=tradicional,
	]{abntex2}

%%%%%% IMPORTAÇÃO DOS PACOTES %%%%%%
\input{preamble/preambulo}

% Informacoes de dados para CAPA e FOLHA DE ROSTO:
\titulo{Estudo de Impedâncias e Instabilidades Coletivas aplicadas aos aceleradores do LNLS.}
\autor{Fernando Henrique de Sá}
\local{Campinas}
\data{2016}
\orientador{Prof. Dr. Antônio Rubens Britto de Castro}
\coorientador[Co-orientador]{Prof. Dr. Sílvio}
\instituicao{%
    UNIVERSIDADE ESTADUAL DE CAMPINAS
    \par
    Instituto de Física Gleb Wataghin (IFGW)
    }
\tipotrabalho{Tese (Doutorado)}
% O preambulo deve conter o tipo do trabalho, o objetivo, o nome da instituição
% e a área de concentração
\preambulo{Tese apresentada ao Instituto de Física da Universidade Estadual
           de Campinas como parte dos requisitos exigidos para a obtenção do
		   título de Doutor em Física, com ênfase em Física de Aceleradores.}

\input{preamble/comandos}

\includeonly{
%content/Chap1-introducao,
content/Chap3-impedancias_e_wakes,
%content/App1-derivacoes,
}

\begin{document}
	% Retira espaço extra obsoleto entre as frases
	\frenchspacing

	%---------- Elementos pré-textuais --------------%
	\pretextual
	\input{preamble/pretextuais}

	%---------- Elementos textuais ------------------%
	\textual

%	\include{content/Chap1-introducao}

\chapter{Introduction} \label{chap:intro}




Most light sources uses synchrotron storage rings where subatomic charged particles, generally electrons, are extracted from materials and accelerated to relativistic energies in order to produce radiation. Among the several types of accelerators the synchrotron is a machine


and depending on the type of accelerator the light may acquire some other important properties for its use as scientific tool. There are several types of accelerator, however, nowadays the most  synchrotron light sources are based in two types. The linear accelerators, used in Free Electron Lasers (FEL) and X-ray Free Electron Lasers (X-FELS), and the synchrotron storage ring accelerators.

In both types of accelerators the light is generated by magnetic devices called insertion devices (IDs) that generates an alternating magnetic field along the particle trajectory which makes them wiggle.


In the latter, ultra-relativistic charged particles are stored in approximately round machines for hours, hence the name storage rings and they generate radiation

  \section{Synchrotron light sources}

  In scientific facilities commomly known as synchrotron lights sources (SLS) the interaction between light and matter is used to study properties of a variaty of materials. Throught techniques involving absortion, reflection, refraction and scattering of light of different 'colors' by the materials under study, scientists can determine their atomic structure and composition.

  The frequency of the light used in these facilities ranges from tera-hertz to hard X-rays and its origin is always related to synchrotron emittion of radiation by charged particles, hence the name of the facility. The light emitted by centripetal acceleration of ultra-relativistic particles has unique properties for use in scientific investigation. Besides its broad spectrum, among the advantages in relation to other methods are the high total flux emitted and the strong collimation.

    \subsection{Types of Light Sources}

    In general we can group syncrotron light facilities in two groups depending on the topology of the accelerators involved: linear and circular. In the linear sources, denominated Free Electron Lasers (FEL), the light is generated by special devices called Insertion Devices (ID) that are put along the straight trajectory of the beam and generates a transverse magnetostatic field with an amplitude that varies sinusoidally with respect to the longitudinal direction. When the beam passes throught this field it wiggles, and synchrotron emittion of radiation happens due to its deflection at each wiggle. The light emitted from successive wiggles interferes in such a way that only photons with specific frequencies survive and the resulting radiation has a spectrum where all the energy is concentrated at very thin peaks around multiples of this resonant frequency. The intensity of these peaks is proportional to the number of particles in the beam and the number of wiggles of the ID field and their bandwidth is proportional to the inverse of the number of wiggles, hence these devices are built with the maximum number of periods that are technically possible. Additionally, the polarization of the radiation is defined by the direction of the magnetic field of the ID. For example, if the field is vertical in relation to the ground, the electrons will oscilate horizontally and the radiation will be horizontally polarized. Circular and elliptical polarizations can also be achieved by changing not only the intensity of the field but also its direction as a function of the longitudinal position. In a real insertion device all these properties of the light can be tuned according to the needs of the experiment to be carried out at the beamline, which makes this devices a very powerful tool for scientific experiments.

    Besides all the amazing properties of the insertion devices, in Free Electrons Lasers it is possible to excite the beam to emit light coherently, hence the name of these facilities. There are several techniques to achieve this and their enumeration or explanation is beyond the scope of this work. The important fact is that besides the high level of coherence of the light in these facilities, the intensity of the photon beam is increased by orders of magnitude with these techniques because it becomes proportional to the square of the number of particles in the beam. The excitation of coherent emittion becomes increasingly difficult as the energy of the photons increase, because ever smaller errors in the fields or decoherences in the electron beam destroy the cascade of the stimulated emittion. This task is so difficult that only in the last decade coherent X-rays where successfully generated by new machines that where built specially for that, the X-FELs. This achievement represented a revolution in the synchrotron radiation community and opened up exciting new possibilities for scientific research.

    Among the several types of circular accelerators we highlight the synchrotron storage rings. There is an abuse of use of the word synchrotron here, so far it meant the nature of emittion of the light in these facilities, but when used to describe this type of accelerator it is related to the synchronicity of the revolution time of the electrons with the electromagnetic field that drives their motion, which is the main mechanism that makes these machines work. In this type of light source radiation the electrons are grouped in several bunches that fill the whole storage ring and are confined in close to circular orbits by deflecting and focusing magnetostatic fields for hours. The radiation used in experiments can be generated by the same fields that deflect the beam (dipoles) or by insertion devices put in empty sections of the ring, called straight sections, just like in FELs, except for the coherent emittion which was never achieved in storage rings due to technical problems.

    While the experiments in X-FELs are performed with only one strong single pulse of radiation that can be generated at a repetition rate of a few hundreads of Hertz, in storage rings the ligth emitted by the bunchs that fill the machine continuously hit the samples and the interaction patterns are recorded for as long as needed to achieve the desired resolution for the experiment. Besides, while in X-FELs it is only possible to have one beamline operating, in storage rings dozens of them can work simultaneously, performing completely different experiments.


    \subsection{Light Source Generations}

    All experiments in light sources are perfomed with the assumption that the properties of the light that hit the samples are known. This means that all analysis assumes the photon beam have a specifc energy, polarization, size and divergence at the interaction point. It is also important to know how many photons will hit the sample per unit of time, in order to compute how long the experiment will take for the emergency of the desired pattern in the collected data. the light beam  almost monochromatic beams of light because in this situation the collection of data and analysis of the interaction with matter is simplified and conclusion can be taken from it. Insertion devices already provide this, however the radiation from dipoles must be filtered and most of the energy emitted is discarded. Besides, several experiments requiseres spatial resolution and this light is generally focused to the minimum spot possible,,   There is a figure of merit that is used to classify the quality of the light of a given light source, the Brightness. It is defined as the averare total flux of photons with energy that falls within a given interval, divided by this interval and by the characteristic volume this beam ocuppies in the transverse phase space.

  \section{Brazilian Synchrotron Light Laboratory}

  The Centro Nacional de Pesquisa em Energia e Materiais (CNPEM) is a brazilian institution located in Campinas-SP that gathers four national laboratories, being the Brazilian Synchrotron Light Laboratory (LNLS) one of them. This laboratory was created in 1987 with the objectives of project, construct and operate a synchrotron light source.

  Such objective was achieved successfully with the creation of UVX, a second generation light source which begun operation with external users in 1997. From them

    \subsection{UVX}
    \subsection{Sirius}
  \section{Collective Effects}
    \subsection{Direct Interaction}
    \subsection{Interaction throught medium}
  \section{Description of the work}

  The main objective of this work was to study the subject of collective effects in electron storage rings, gathering the knowledge generated by the community in the last years, and apply this knoledge to study these effects on Sirius storage ring, with estimatives of instabilities thresholds among other collective phenomena commom to this type of accelerators.


\chapter{Concepts of Single Particle Dynamics}

Before the study of collective effects in storage ring is necessary to understand some concepts of single particle dynamics.

  \section{Storage Ring Main Devices}

  The first and most important concept is that of a storage ring. As its name suggests, it is a machine that keeps charged particles in almost circular revolution trajectories for millions of turns with almost constant energy. How these particles are injected in this machine or accelerated to its nominal energy is beyond the scope of this work.

  Connected to the concept of a storage ring is the one of the reference orbit. This special closed orbit is the one that an idealized particle with the storage ring nominal energy would follow if it had the correct initial conditions. In practice the trajectories of all particles stored in the machine will be close to it. For this reason the reference orbit is chosen to be the origin of the reference frame, defining a curved coordinate system that moves along the ring, with one longitudinal coordinate tangent to the local orbit and two transverse coordinates perpendicular to it.

  Besides, all the components of a storage ring are aligned according to this special orbit in such a way that their center, symmetry points or axis coincide with transverse sections of the reference orbit.

  The storage ring task of keeping particles confined for such long times is achieved with the aim of electromagnetic fields to guide and replenish the energy lost by the particles due to synchrotron radiation emittion and an integrated ultra high vacuum system to increase their mean free path, minimizing scattering by gas molecules and consequent loss.

  Below we describe some of the main components of a storage ring.

    \subsection{Dipoles}

    Dipoles are devices that generate a static magnetic field that is non-zero at the reference orbit under ideal conditions. This is the only magnet that have such characteristic, in other words, this magnet is the only type of magnet that must afect the trajectory of the idealized particle that defines the reference orbit. It acts on the particle throught the Lorentz force, such as other magnets, bending its trajectory. Ideally, the local curvature that a dipole introduces in the reference particle path must be equal to the curvature of the reference orbit and the reference orbit must be curved only at places where there is a dipole magnetic fields. Shortly, dipoles are the responsible for the ring topoly of a storage ring.

    \subsection{Multipoles}

    Apart from dipoles, all the other magnets are placed at positions where the reference orbit is straight. Therefore, they do not act on idealized reference orbit and must generate a null magnetic field at the positions of the reference orbit. Their function is to confine the movement of the realistic particles in trajectories close to the reference orbit.

    Multipoles are grouped in several types, according to the characteristics of the field they gerenerate in the vicinity of the reference orbit.For example, an ideal quadrupole generates fiels whose transverse components grows linearly with the transverse coordinates of the local reference system and have no longitudinal fields, Sextupoles generate quadratic fields, Octupoles, cubic, and so on. These properties are not exactly true for real magnets, but in gerenal are a good approximation.

    The quadrupoles are the most important multipoles in a storage ring. Because their magnetic field components vary linearly with the particles position in relation to the reference orbit, they act as magnetic lenses, focusing and defocusing the particles beam. Together with the dipoles, they define the main properties of a storage ring, as the particles average energy, the transverse beam emittance, and beam sizes along the ring. These three factors combined define the brilliance of the photons, the figure of merit of a light source.

    It is important to mention that dipoles also work as lenses for the beam. As the quadrupoles, they may have transverse field components that vary linearly with the displacement from the reference orbit, being the only differences the fact that this orbit is curved and the field is non-zero at the reference orbit. Actually, even a dipole with uniform field may focus particles, due to the curvature of the reference system that introduces differences in path length in non-zero field regions for different transverse displacements, or due to edge fields generated by the finite length of the magnet.

    Dipoles work as spectrometers, deflecting more or less particles with less or more energy than the reference particle, which means they could not sustain these particles stored because the total deflection angle would not be $2\pi$ rad and they would spiral in or out, hitting the vaccum chamber. Quadrupoles are arranged to correct this intrinsic limitation of the dipoles, adding or subtracting liquid deflection in one turn for particles with more or less energy. This force particles to have different closed orbits depending on their energy, but at least maintain the chance of them to remain stable. However, quadrupoles also suffer from chromatic aberrations, focusing more or less the particles, depending on their energy. This difference in focusing makes particles oscillate more or less around their closed orbit, changing their fundamental resonance frequency. This is not a fundamental problem, but in almost all modern storage rings it is impossible to store particles with only dipoles and quadrupoles. Sextupoles can correct that effect if placed at the right positions along the ring because of their non-linear magnetic field. They also introduce chromatic effects, but for the modern storage rings this does not affect the capability of storaging particles.

    Sextupoles are needed, but they introduce several complications for the design of a storage ring, because their non-linear fields introduce chaos in some regions of the particles phase space. More sextupoles or higher order multipoles can be introduced to avoid chaos as much as possible and also to help correcting higher order chromatic effects, but this analysis is beyond the scope of this work.

    \subsection{RF Cavity}

    Each turn the electrons lose energy due to synchrotron radiation which must be replenished periodically in order for them to remain in stable orbits, with energy close to the nominal energy of the storage ring. The magnetostatic components described above cannot perform such a task neither any other component or method relying on static electromagnetic fields of any kind, because according to Maxwell equations and the Lorentz equation, the liquid energy transfered to charged particle by static fields in one turn over the ring must be zero. Then the laws of physics constraint that it is necessary to rely on time dependent electromagnetic fields to replenish the energy of the electrons. The way this is accomplished in a storage ring is through the use of devices called RF cavities.

    RF cavity is a jargon for a cylindrical electromagnetic cavity with the lowest Transverse Magnetic (TM01) mode in the range of radiofrequency. Cavities for use in storage rings must have at least two small holes in its axis for the beam passage and one other hole to couple the cavity with an external source to feed the mode TM01 with energy. This energy is transfered to the particles in the storage ring throught the almost homogeneous longitudinal eletric field of TM01 when the particles passes throught the cavity.

    \subsection{Vacuum System}

    The vacuum system is responsible for creating a compact region around the reference orbit in the whole machine with very low pressure, which minimize collisions of the stored charged particles with gas molecules and, consequently, increase the average time particles can be stored with stable movement. Quantitatively, the average pressure of a storage ring must be lower than 1 nTorr for the average stored time of the particles to be of the order of a few dozens of hours.

    The vacuum system is composed of two main subsystems, the vacuum vessel, which defines the boundaries of the electrons atmosfere with the environment, and vacuum pumps to maintain the desired difference in pressure between the two environments. Most of the extension of the vacuum vessel is composed of straight and long chambers with a specific cross section, constant along the extension of the chamber. They are made of metals due to several desirable properties these materials presents, such as high heat and electrical conductivity, maleability, high acceptance to yelding and brasing and high resistence to pressure. Among them we highlight implications of the high electrical conductivity due to its importance for this work.


  \section{Transverse Dynamics}

  After the introduction of the main components, it is convenient to describe in general terms how is the movement of the stored particles. These particles are ultra-relativistic electrons with energy of the order of a few \si{GeV}, and most of their velocity is always in the direction of the tangent of the ideal orbit. Gererally there are approximately hundreds of billions electrons grouped in several bunches along the reference orbit, each bunch having a few milimiters length and transverse sizes of the order of dozens of microns. Each electron is under the influence of a variaty of electromagnetic fields (gravity can be neglected), coming from the static magnetic fields of the dipoles and multipoles, the radiofrequency field of the RF cavity, the direct fields of other electrons in the same bunch and the fields scattered by the vaccum vessel, generated by other electrons in the same bunch, in other bunches or even by themselves in previous turns. Also, they emit synchrotron radiation which makes them lose energy.

  The path of understanding and describing the dynamics of the stored particles begin with an approximation that neglect the effects of their self-fields, i.e. their interaction with each other, with the vaccum chamber and with the residual molecules in their atmosphere. In this framework the only forces acting on the particles are the magnetic fields of the dipoles and multipoles and the longitudinal electric field of the RF Cavity and the only way they can lose energy is throught synchrotron radiation emittion.

    \subsection{Hamiltonean Approximation}

    When such calculations are performed for current synchrotrons it is noticeable that the dynamics of the longitudinal motion is much slower than the dynamics of the transverse motion. As an example, in the Sirius storage ring particles take approximately 131 revolutions around the ring to complete one turn around the fixed point in the longitudinal direction while they oscillate 49 times per revolution around the fixed point in the transverse plane. This property makes it possible to separate the study of the longitudinal plane from the transverse one, considering the energy deviation of one particle as a constant parameter in the transverse equations of motion. The effects of the radiation energy loss are even slower than the longidudinal motion, taking a few thousands of turns in the ring to significantly change the transverse motion.

    Neglecting the energy variations of the particles, and the randonnes of the radiation emittion, the motion of the particles can be described by a constant hamiltonean in the Frenet-Serret coordinate system defined by the ideal orbit. Procceding in the approximations, considering the paraxial motion of the particles around the closed orbit, this hamiltonean can be simplified to a quadratic form in the momenta coordinates.

    This Hamiltonean generates two second order coupled and non-linear equations of motion for the transverse coordinates of motion that accurately describes the short and mid term stability of the particles. Most of the non-linearities and coupling in these equations come from the magnetic fields of the components along the ring, being the other contributor the curvature of the reference orbit and the energy deviation of each particle. At this stage of the simplification of the problem the dynamics of the electrons still is very complicated, mainly for storage rings such as Sirius, with several and very strong Sextupoles that introduces chaos in the system in regions of the phase-space that are close to the fixed point.

    \subsection{Linear Equations of Motion}

	With further approximations, considering only the terms of the equations of motion that are linear with the phase-space coordinates and eliminating all coupling between the two transverse directions of motion, the analysis of the dynamics becomes simple enough to allow its complete understanding, with analytical solutions to the equations of motion and physically significant parametrizations, that summarizes and simply describes a given machine. In this regime, the transverse movement of the electron is only dependent on the fields of dipoles and quadrupoles.

	Looking back at the start of this section and reviewing all the approximations, at first sight it seems that the region of validity of these linear equations is so limited that their understanding is useless. However that is not what is observed in practice, because storage rings are carefully designed to maximize the validity of this linear behavior: the position, number and strength of all magnets are so well tuned that nonlinearities cancel each other. This approach is used because the general nonlinear dynamics is so complicated that there is no theoretical background to understand stability and confidence to build a machine that is intrinsically non-linear. This is a subject that is being investigated for a long time in the synchrotron comunity, but so far none light source was ever built based in a non-linear storage ring.

	Another important point to justify the study of these linear equation is that, luckly, for synchrotron radiation generation the smaller the transverse size and divergence of the electron beam the better, which means most particles will stay for most of the time in a very small region of approximately hundreads of microns around the fixed point, where only quadrupoles have a significant effect. Besides, if a particle experience large transverse oscillations, damping effects that arise due to synchrotron radiation emittion will bring them close to the fixed point in a few dozens of miliseconds.


    \subsection{Betatron Function and Phase Advance}

	The solution of the homogeneous part of the linear equations of motion can be parametrized in the such form:
	\begin{align} \label{eq:betatron_motion}
		u(s) &=& \sqrt(J\beta_u(s)) \cos(\mu_u(s) - \phi)
	\end{align}
	where $u$ stands for both, $x$ or $y$, $\beta_u(s)$ is called the betatron function and depends only on the the magnetic lattice and $\mu_u(s)$ is called phase advance and its relation to the betatron function is given by
	\begin{align}
		\mu'_u(s) &=& \frac{1}{\beta_u(s)}.
	\end{align}
	The constants $\phi$ and $J$ depend on the initial conditions. It can be shown that:
	\begin{equation}
		J = \gamma_u(s)u^2(s) + 2\alpha_u(s)u(s)u'(s) + \beta_u'(s)u'^2(s)
	\end{equation}
	where $\alpha_u(s) = -\frac{\beta_u(s)}{2}$ and $\gamma_u(s) = \frac{1+\alpha_u^2(s)}{\beta_u(s)}$, which represents the equation of an ellipse in phase space with $J$ being the area of such ellipse.

	The relevance of this parametrization is that there are several very important practical informations regarding the properties and responses to perturbations of the beam that can be extracted directly from the betatron function. It can be seen from equation \label{eq:betatron_motion} that the maximum excursion a given particle can experience in a fixed longitudinal point of the ring is proportional to the square root of the betatron function. Analogously, averages in an ensemble of particles in equilibrium show that the beam size of the distribution must also be proportional to the square root of betatron function at that location. Besides, the ratio between the maximum amplitude of movement in two different positions is proportional to the ratio of the square root of the betatron functions at the two locations, a property that is fundamental in the process of defining the transverse sizes of the vaccum chamber of a storage ring. For example, lets suppose the maximum betatron function of a lattice is \SI{16}{\meter} and at this place the vaccum chamber has an internal dimension of \SI{12}{\milli\meter}, in another place, where the betatron function is only \SI{1}{\meter} the vaccum chamber can be much smaller, only \SI{3}{\milli\meter}, the vaccum chamber can

	Another important property is related

    \subsection{Dispersion Function}
    \subsection{Envelope Equations}
    \subsection{Chromaticity and Action Dependent Tune-shift}
  \section{Longitudinal Dynamics}
    \subsection{Phase Stability Principle}
    \subsection{The Potential-Well}
    \subsection{Linear equations of motion}
  \section{Radiation Damping and Equilibrium Parameters}
    \subsection{Longitudinal Damping}
    \subsection{Transverse Damping}
    \subsection{Quantum Excitation and Equilibrium parameters}
    \subsection{Fokker-Planck Equation}

\chapter{Wake-Fields and Impedances}
  \section{Wake-Fields}
    \subsection{Interaction Mechanisms}
    \subsection{Causality and Catch-up Distance}
    \subsection{Wake-function Definition}
    \subsection{Panofsky-Wenzel Theorem}
    \subsection{Symmetry Analysis}
    \subsection{Potential of Bunch of particles}
  \section{Impedances}
    \subsection{Impedance Definition}
    \subsection{Impedance Properties}
      \subsubsection{Causality}
      \subsubsection{Passivity}
      \subsubsection{Energy Loss}
  \section{Classification of Impedances and Wake-functions}
    \subsection{As Resonators}
      \subsubsection{Broad-band}
      \subsubsection{Narrow-Band}
    \subsection{As circuit components}
      \subsubsection{Inductive}
      \subsubsection{Capacitive}
      \subsubsection{Resistive}
    \subsection{According to its source}
      \subsubsection{Resistive Wall}
      \subsubsection{Geometric}
      \subsubsection{Coherent Synchrotron Radiation}
  \section{Impedance Calculation}
    \subsection{Analytic Methods}
      \subsubsection{Field Matching Technique}
      \subsubsection{Perturbative Method}
      \subsubsection{Parabolic Equation}
    \subsection{Numeric Methods}
      \subsubsection{Frequency Domain Solvers}
      \subsubsection{2D Time domain Solvers}
      \subsubsection{3D Time domain Solvers}

\chapter{Collective Effects}
  \section{Energy Loss}
  \section{Potential-Well Distortion}
  \section{Tune-shifts}
    \subsection{Coherent Tune-shifts}
    \subsection{Incoherent Tune-shifts}
  \section{Instabilities}
    \subsection{Multi-Turn Instabilities}
    \subsection{Single-Turn Instabilities}
  \section{Landau damping}
  \section{Analytical Treatment}
    \subsection{The Linearized Fokker-Planck Equation}
      \subsubsection{Stationary Solution: Haissinski Equation}
      \subsubsection{Modal expantion}
        \paragraph{Head-tail modes}
      \subsubsection{Solution for Gaussian Bunches}
      \subsubsection{Low Current Limit: Multi-Turn Instabilities}
      \subsubsection{High Current Limit: Mode Coupling Instabilities}
    \subsection{The Microwave Instability}
    \subsection{Strong Head-tail instability}
  \section{Numerical Treatment}
    \subsection{Tracking Codes}
      \subsubsection{Lump of Impedance Kicks}
      \subsubsection{Slicing and particle deposition}
      \subsubsection{Single-Bunch tracking codes}
      \subsubsection{Multi-Bunch tracking codes}


\chapter{Experimental Methods}
  \section{Impedance Measurement}
    \subsection{Direct Measurement}
      \subsubsection{Wire technique}
      \subsubsection{Double wire technique}
    \subsection{Beam Measument}
      \subsubsection{Single-bunch Current Dependent Tune-shifts}
      \subsubsection{Multi-bunch Current Dependent Tune-shifts}
      \subsubsection{Single-bunch Turn-by-Turn measurements}
      \subsubsection{Orbit bump method}
      \subsubsection{response matrix fitting}
      \subsubsection{Instability Threshold Measurements}
  \section{Instability Cures}
    \subsection{Landau Cavity}
    \subsection{Chromaticity}
    \subsection{Cavity power absorbers}
    \subsection{Cavity temperature adjustments}
    \subsection{Bunch-by-Bunch Feedback System}
      \subsubsection{How it works}
      \subsubsection{Possible Experiments}
        \paragraph{Grow-Damp Experiments}
        \paragraph{Tune measurement}
        \paragraph{Beam Response Function Measurement}
      \subsubsection{Main Limitations}

\chapter{Methodology}
  \section{}

\chapter{Results}
  \section{Components Impedance Modelling}
    \subsection{Multi-Layer Resistive Wall}
      \subsubsection{Pipe}
      \subsubsection{Ceramic Chambers}
      \subsubsection{Thin Chambers}
    \subsection{Geometric Transitions}
      \subsubsection{2D-Calculations}
        \paragraph{BC Chamber}
        \paragraph{RF Cavity taper}
        \paragraph{Undulators Tapers}
      \subsubsection{3D-Calculations}
        \paragraph{BPMs}
        \paragraph{Bellows}
        \paragraph{Radiation Masks}
    \subsection{Coherent Synchrotron Radiation (CSR)}
  \section{Impedance Budget}
    \subsection{Longitudinal Impedance}
      \subsubsection{Effective Z/n}
      \subsubsection{Multi-bunch Kloss and Dissipated Power}
    \subsection{Vertical Impedance}
    \subsection{Horizontal Impedance}
  \section{Simulations and Instabilities Thresholds}
    \subsection{Frequency Domain Calculations}
      \subsubsection{Vertical Plane}
        \paragraph{Single-bunch Tune-Shifts}
        \paragraph{Multi-bunch Tune-Shifts}
        \paragraph{Coupled-Bunch Instabilities}
        \paragraph{Single-Bunch Instabilities}
      \subsubsection{Horizontal Plane}
        \paragraph{Single-bunch Tune-Shifts}
        \paragraph{Multi-bunch Tune-Shifts}
        \paragraph{Coupled-Bunch Instabilities}
        \paragraph{Single-Bunch Instabilities}
      \subsubsection{Longitudinal Plane}
        \paragraph{Multi-Bunch Instabilities}
        \paragraph{Single-Bunch Instabilities}
    \subsection{Time Domain Calculations}
      \subsubsection{Longitudinal Plane}
      \subsubsection{Vertical Plane}
      \subsubsection{Horizontal Plane}


	%\part{Fundamentos}
    \include{content/Chap2-fisica_aceleradores}
    \include{content/Chap3-impedancias_e_wakes}
	%\part{Contribuições}
	\include{content/Chap4-modelo_impedancia}
    \include{content/Chap5-instabilidades}

	% Finaliza a parte no bookmark do PDF, para que se inicie o bookmark na raiz
	\bookmarksetup{startatroot}%

	%\chapter*[Conclusão]{Conclusão}
	%\addcontentsline{toc}{chapter}{Conclusão}
	%\lipsum[1-5]


	% --------- Elementos pós-textuais --------------&
	\postextual
	\input{preamble/postextuais}

\end{document}
